


# Data import 


```{r}

library(tidyverse)
library(metafor)
library(ggthemes)
library(cowplot)
library(scales)
library(knitr)
library(broom)
library(dplyr)
library(readxl)
library(gsheet)
library(janitor)
library(ggforce)

fls_dat <- read_csv("fls_data.csv") %>% 
  filter(mean_yld != "NA") %>% 
  filter(mean_sev != "NA") %>% 
  filter(study!= 60) %>% 
  group_by(study) %>% 
  mutate(difer = max(mean_sev) - min(mean_sev)) %>% 
  filter(difer>5) #selecting studies with more than 5% difference in disease severity across treatments
head(fls_dat)

length(unique(fls_dat$study))

```

## Creating moderators


### yield class

Here we will group the yield data into two production situations, low or high yield, based on median of yields across trials.

  
```{r, message=FALSE, warning=FALSE}


summary(fls_dat$mean_yld)

fls_dat <- fls_dat %>%
  mutate(yield_class = case_when(mean_yld <= 3352 ~ "Low",
                         mean_yld > 3352 ~ "High"))

a1 = fls_dat %>% 
  group_by(study, yield_class) %>% 
  summarise() %>%
  tabyl(yield_class)
a1 
```

### Disease class

Here we will group the severity data into two disease pressure situations, low or high, based on median of disease severity in the Check.

```{r, message=FALSE, warning=FALSE}

summary(fls_dat$sev_check) # the median value of the FLS severity in the untreated plots was 34.57%

fls_dat <- fls_dat %>%
  mutate(sev_class = case_when(sev_check <= 34.57 ~ "Low",
                         sev_check > 34.57 ~ "High"))

a2 = fls_dat %>% 
  group_by(study, sev_class) %>% 
  summarise() %>%
  tabyl(sev_class)
a2
```

## Population-average mixed model estimates

We will use the `lmer` function of the `lme4` to fit three different kinds of mixed models: random intercepts and slopes, random intercepts only and random slopes only.

  
  
```{r, message=FALSE, warning=FALSE}
library(lme4)

# null model
mix_yld <- lmer(mean_yld ~ 1 + (1 | study), data = fls_dat, REML = F)

# random intercept and slopes
mix_yld1 <- lmer(mean_yld ~ mean_sev + (mean_sev | study), data = fls_dat, REML = F)

# random slopes
mix_yld2 <- lmer(mean_yld ~ mean_sev + (1 | mean_sev), data = fls_dat, REML = F)

# random intercepts
mix_yld3 <- lmer(mean_yld ~ mean_sev + (1 | study), data = fls_dat, REML = F)
```

Here we can check which model best fitted the data based on the lowest AIC, which was the one with both intercepts and slopes as random effects.

```{r, message=FALSE, warning=FALSE}
AIC(mix_yld, mix_yld1, mix_yld2, mix_yld3)
```

```{r}
summary(mix_yld1)

```


```{r}
confint.merMod(mix_yld1, method = "Wald")

```


### Effect of baseline sev 

Let's include an interaction term and test whether variance was significantly reduced based on likelihood ratio test. 

```{r}
mix_yld5 <- lmer(mean_yld ~ mean_sev * sev_class + (mean_sev | study), data = fls_dat, REML = F)
```

```{r}
AIC(mix_yld1, mix_yld5)
```

```{r}
anova(mix_yld1, mix_yld5, test = "Chisq")
```

```{r}
summary(mix_yld5)
```


```{r}
confint(mix_yld5) 
```


### Effect of yield class 

Let's include an interaction term and test whether variance was significantly reduced based on likelihood ratio test. 

```{r warning=FALSE}
mix_yld8 <- lmer(mean_yld ~ mean_sev * yield_class + (mean_sev | study), data = fls_dat, REML = F)


```

```{r}
AIC(mix_yld1, mix_yld8)
```

```{r}
anova(mix_yld1, mix_yld8, test = "Chisq")
```

```{r}
summary(mix_yld8)
```



```{r, message=FALSE, warning=FALSE}

library(emmeans)
library(multcomp)
cld(emmeans(mix_yld8, ~ mean_sev * yield_class))
```

Extract the random coefficients (BLUES).
  
  
```{r, message=FALSE, warning=FALSE}
blup <- coef(mix_yld1)$study
colnames(blup) <- c("Intercept", "Slope")

summary(blup)
```


 Calculate the interdecile range for the BLUEs of the slopes and intercepts
 
 
```{r, message=FALSE, warning=FALSE}
# Intercept
dec90_i <- quantile(blup$Intercept, probs = c(.9))
dec10_i <- quantile(blup$Intercept, probs = c(.1))
dec90_i - dec10_i

# Slopes
dec90_s <- quantile(blup$Slope, probs = c(.9))
dec10_s <- quantile(blup$Slope, probs = c(.1))
dec90_s - dec10_s
```

## Correlation coefficient

We firstly summarize the Fisher's z as the effect size for the study of the strength of the association between FLS severity and soybean yield. 

```{r, message=FALSE, warning=FALSE}
cor_yld_sev <- fls_dat %>% 
  group_by(study) %>% 
  do(tidy(cor.test(.$mean_sev, .$mean_yld), method = "pearson"))
cor_yld_sev
summary(cor_yld_sev$estimate)
```

```{r}
hist_pears <- ggplot(cor_yld_sev, aes(estimate)) + 
  geom_histogram(bin = 0.1, binwidth = 0.1, color = "black" , fill = "black",
                 alpha = 0.1) + 
  theme_half_open()+
  theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12))+
  labs(x = expression("Pearson's correlation coefficient" ~italic("r")), 
                      y = "Frequency")

hist_pears

```


Let's extract the first row of each study from the `fls_dat` data frame and then combine with the new `cor_yld_sev` data frame that contains the correlation statistics. We will add a new column (n) for the number of data points per study using the `mutate` function.

```{r}
fls_dat2 = fls_dat %>% 
  group_by(study) %>% 
  filter(row_number() == 1)

fls_dat3 <- full_join(cor_yld_sev, fls_dat2, by = "study") %>% 
           mutate(n2 = parameter + 2)  

yield_max <- fls_dat %>%
  filter(mean_yld != "NA") %>% 
  group_by(study) %>% 
  summarize(max_yield = max(mean_yld))

# Grouping the yield max information in a new column
fls_dat3 <- left_join(fls_dat3, yield_max) %>% 
  mutate(yield_class = case_when(max_yield <= 3352 ~ "low",
                         max_yield > 3352 ~ "high")) %>% 
  mutate(sev_class = case_when(sev_check <= 34 ~ "low",
                         sev_check > 34 ~ "high"))
fls_dat3
```

The Fisher's z was used as effect-size because of its better statistical property than the Pearson's r. We obtain the Fisher's z and sampling variance of each study with the `escalc` function of the `metafor` package that calculates and adds them to the data frame. Note that the effect-size and sampling variance are indicated by `yi` and `vi`, the standard notations used in `metafor` when using the `escalc` function. Let's see how the data frame looks like.
 

```{r, message=FALSE, warning=FALSE}
library(metafor)
fls_dat4 <- escalc(measure = "ZCOR", ri = estimate, ni = n2, data = fls_dat3)

```

```{r}
summary(fls_dat4$yi)
data.frame(fls_dat4)
```

```{r}
hist_fisher <- ggplot(fls_dat4, aes(yi)) + 
  geom_histogram(bin = 0.1, binwidth = 0.2, color = "black" , fill = "black",
                 alpha = 0.1) + 
  theme_half_open()+
  theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12))+
  labs(x = expression("Fisher's transformation of"~ italic("r")~ "("~italic("Z" [r])~")"), 
                      y = "Frequency")
hist_fisher


library(patchwork)
(hist_pears + hist_fisher) +
  plot_layout(nrow = 1)+
  plot_annotation(tag_levels = "A")

ggsave("Figures/Corr_coeff.png", height=3, width=8, dpi = 600, bg = "white")
```


## Overall Fisher's z

A [random-effects](http://www.metafor-project.org/doku.php/tips:rma.uni_vs_rma.mv) meta-analytic model was fitted to these data using a maximum likelihood estimator for the amount of heterogeneity. 

```{r, message=FALSE, warning=FALSE}
fls_cor_yld <- rma.uni(yi, vi, method = "ML", data = fls_dat4)
summary(fls_cor_yld)
```


Back-transform z to obtain overall mean r.

```{r, message=FALSE, warning=FALSE}
pred_fls <- predict(fls_cor_yld, transf = transf.ztor)
pred_fls
```



## Effect of moderators

The random-effects model fitted previously assumes that the heterogeneity in the true correlation coefficients (Fisher's z) is purely random. However, there may be differences among the individual effects that are (at least in part) related to study-specific variables. These variable can be treated as "moderators" in the model. We considered here: disease and yield levels.

The mixed-effect models test one moderator variable, each at a time, as a fixed effects. The goal was to examine the extent that the moderators included in the model influence the size of the average true effect. The heterogeneity among the true effect-sizes is evaluated based on significance of the Cochran Q test and the *I*<sup>2</sup> index that measures the extent of heterogeneity of the true effect-sizes.



### disease pressure

```{r}

fls_cor_yld_sev2 <- rma.uni(yi, vi, mods = ~sev_class, method = "ML", data = fls_dat4)
fls_cor_yld_sev2

```


### yield class

```{r}
fls_cor_yld_yld2 <- rma.uni(yi, vi, mods = ~ yield_class, method = "ML", data = fls_dat4)
fls_cor_yld_yld2
```


