


# Data import 


```{r}

library(tidyverse)
library(metafor)
library(ggthemes)
library(cowplot)
library(scales)
library(knitr)
library(broom)
library(dplyr)
library(readxl)
library(gsheet)
library(janitor)
library(ggforce)

fls_dat <- read_csv("fls_data.csv") %>% 
  filter(mean_yld != "NA") %>% 
  filter(mean_sev != "NA") %>% 
  filter(study!= 60) %>% 
  group_by(study) %>% 
  mutate(difer = max(mean_sev) - min(mean_sev)) %>% 
  filter(difer>5) #selecting studies with more than 5% difference in disease severity across treatments
head(fls_dat)

length(unique(fls_dat$study))
```


# Data visualization

## Histograms

The histograms below summarize the distribution of the two variables: FLS severity and soybean yield. 

```{r, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
hist_sev <- ggplot(fls_dat, aes(mean_sev)) + 
  geom_histogram(bin = 1, binwidth = 4.2, color = "black" , fill = "black",
                 alpha = 0.1) + 
  geom_vline(xintercept = 19.46,
             size = 1.2,
             linetype = 2)+
  scale_x_continuous(breaks = c(0, 25,50,75,100), limits = c(0, 100)) +
  theme_half_open()+
  theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12))+
  labs(x = "FLS severity (%)", y = "Frequency")
  
hist_yld <- ggplot(fls_dat, aes(mean_yld)) + 
  geom_histogram(bin = 1, binwidth = 200, color = "black" , fill = "black",
                 alpha = 0.1) + 
  geom_vline(xintercept = 3327,
             size = 1.2,
             linetype = 2)+
  scale_y_continuous(breaks = c(0,20,40,60), limits = c(0, 60)) +
  theme_half_open()+
  theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12))+
  labs(x = "Yield (kg/ha)", y = "Frequency")

library(patchwork)
(hist_sev + hist_yld) +
  plot_layout(nrow = 1)+
  plot_annotation(tag_levels = "A")

ggsave("Figures/histograms.png", height=3, width=8, dpi = 600, bg = "white")

```

## Ordinary Regressions

Ordinary regression for each study.

```{r fig.height=12, fig.width=12, warning=FALSE}
ggplot(fls_dat, aes(mean_sev, mean_yld))+
       geom_point(shape = 1)+
       stat_smooth(method = lm, fullrange=TRUE, se = F, col = "black")+
       ylab("Yield (kg/ha)")+
       xlab("FLS Severity (%)")+
        ylim(0,6000)+
      theme_half_open()+
      theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12))+
       facet_wrap(~ study, ncol = 5, scales = "fixed")
ggsave("Figures/grid_lines.png", height=12, width=12, dpi = 600, bg = "white")

```


```{r}
lines_kg = ggplot(fls_dat, aes(mean_sev, mean_yld))+
      geom_smooth(method="lm", fullrange= T, se=F, size=0.7, color="grey80", aes(group = factor(study)))+
     # geom_point(alpha = 0.5, shape = 1)+
      ylab("Yield (kg/ha)")+
      xlab("FLS Severity (%)")+
      ylim(0,6000)+
      xlim(0,100)+
      theme_half_open()+
      theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12))
lines_kg
```


## Regression coefficients

```{r}
reg_dc = fls_dat %>% 
  group_by(study, year) %>% 
  summarise(intercept = lm(mean_yld~mean_sev)$coefficients[1],
            slope = lm(mean_yld~mean_sev)$coefficients[2],
            r2 = summary(lm(mean_yld~mean_sev))$r.squared,
            sigma = summary(lm(mean_yld~mean_sev))$sigma) %>%
  mutate(Dc = (slope/intercept)*100) %>% 
  filter(Dc<0.5)

reg_dc
summary(reg_dc$intercept)
summary(reg_dc$slope)
```


### Distribution of intercepts and slopes

```{r}
int = reg_dc %>% 
  ggplot(aes(intercept))+
  geom_histogram(color = "black" , fill = "black",
                 alpha = 0.1, bins = 15) + 
  theme_half_open()+
  labs(y = "Frequency", x = "Intercept")+
    theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12))


slope = reg_dc %>% 
  ggplot(aes(slope))+
geom_histogram(color = "black" , fill = "black",
                 alpha = 0.1, bins = 15) +   theme_half_open()+
  labs(y = "Frequency", x = "Slope")+
    theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12))
   

```

## Population-average regression

Using intercepts and slopes with respective 95% CI.

```{r}
geral = fls_dat %>% 
ggplot(aes(mean_sev, mean_yld))+
      geom_smooth(method="lm", fullrange= T, se=F, size=0.7, color="grey80", aes(group = factor(study)))+
      ylab("Yield (kg/ha)")+
      xlab("FLS Severity (%)")+
  ylim(0,6000)+
  xlim(0,100) +
  theme_half_open()+
  geom_abline(aes(intercept = 3719.91, slope = -19.08), size = 1.3, linetype = "solid") +
  geom_abline(aes(intercept = 3395.91, slope = -23.96), size = 1.0, linetype = "dashed") +
  geom_abline(aes(intercept = 4045.61, slope = -14.22), size = 1.0, linetype = "dashed")+
  theme(axis.title = element_text(size=12),
        axis.title.y = element_blank(),
        axis.text = element_text(size=12))
geral

```


```{r}
library(patchwork)
(lines_kg + geral)/(int + slope) +
  plot_layout(nrow = 2)+
  plot_annotation(tag_levels = "A")
ggsave("Figures/coefficients.png", height=10, width=10, dpi = 600, bg = "white")

```


### Yield class effect on Intercepts

High Yield 

```{r}
high <- ggplot(fls_dat, aes(mean_sev, mean_yld)) +
  geom_smooth(method="lm", fullrange= T, se=F, size=0.7, color="grey90", aes(group = factor(study)))+
  ylim(0, 6000) +
  xlim(0, 100) +
  labs(title = "Baseline yield: High",
    x = "FLS Severity (%)",
    y = "Soybean yield (kg/ha)") +
  theme_half_open() +
  geom_abline(aes(intercept = 3842.69, slope = -16.20), size = 1.5, linetype = "solid") +
  geom_abline(aes(intercept = 3557.12, slope = -21.45), size = 1.5, linetype = "dashed") +
  geom_abline(aes(intercept = 4126.21, slope = -10.81), size = 1.5, linetype = "dashed")+
  theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12),
        plot.title = element_text(hjust = 0.5))
high
```
 
Low yield

```{r}
low <- ggplot(fls_dat, aes(mean_sev, mean_yld)) +
  geom_smooth(method="lm", fullrange= T, se=F, size=0.7, color="grey90", aes(group = factor(study)))+
  ylim(0, 6000) +
  xlim(0, 100) +
  labs(title = "Baseline yield: Low",
    x = "FLS Severity (%)",
    y = "Soybean yield (kg/ha)") +
  theme_half_open() +
  geom_abline(aes(intercept = 3455.11, slope = -14.38), size = 1.5, linetype = "solid") +
  geom_abline(aes(intercept = 3060.12, slope = -23.29), size = 1.5, linetype = "dashed") +
  geom_abline(aes(intercept = 3847.69, slope = -5.3), size = 1.5, linetype = "dashed")+
  theme(axis.title = element_text(size=12),
        axis.title.y = element_blank(),
        axis.text = element_text(size=12),
        plot.title = element_text(hjust = 0.5))
low
```


```{r fig.height=3, fig.width=8}
library(patchwork)
(high + low) +
  plot_layout(nrow = 1)+
  plot_annotation(tag_levels = "A")

ggsave("Figures/baseline_yld.png", height=4, width=8, dpi = 600, bg = "white")
```

## Economic Threshold


```{r}
cost = seq(30, 80,length.out = 200)
lambda = c(0.25, 0.50, 0.75)
soybean = seq(200, 700,length.out = 200)
a = 0.0051
```



```{r}
economic = expand.grid(cost = cost,soybean = soybean, lambda = lambda, a = a) %>% 
  mutate(econ_tresh = ((cost/(soybean*a))*lambda)) %>% 
  mutate(lambda = paste0(lambda,"% of Control")) 
```


```{r}
surface = economic %>% 
  mutate(efficacy = case_when(lambda == "0.25% of Control" ~ "25% of Control",
                              lambda == "0.5% of Control" ~ "50% of Control",
                              lambda == "0.75% of Control" ~ "75% of Control")) %>% 
  ggplot(aes(cost, soybean, fill = econ_tresh))+ 
  geom_raster(alpha = 0.85)+
  scale_fill_viridis_b(option = "B", 
                       guide = guide_colorbar(barwidth = 15, barheight = 0.3),
                       breaks = seq(0, 60, by =5)
                       )+
  facet_grid(~efficacy)+
  theme_minimal_grid()+
  labs(y = "Soybean price (USD/metric ton)",
       x = "Cost (USD/ha)",
       fill ="Economic Damage Threshold (%)" )+
  theme(legend.position = "top",
        legend.justification = 0.5)
surface
ggsave("Figures/EDT.png", height=4, width=8, dpi = 600, bg = "white")

```

